COG-ED Manuscript

### 2022-02-03 06_Paper/COG-ED/Manuscript.Rmd
added comment

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
<!--CS: Zitation hinzufügen?
 @Article{,
    title = {{lmerTest} Package: Tests in Linear Mixed Effects Models},
    author = {Alexandra Kuznetsova and Per B. Brockhoff and Rune H. B.
      Christensen},
    journal = {Journal of Statistical Software},
    year = {2017},
    volume = {82},
    number = {13},
    pages = {1--26},
    doi = {10.18637/jss.v082.i13},
  }--> 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.

>>>>

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
<!--CS: Zitation hinzufügen?
 @Article{,
    title = {{lmerTest} Package: Tests in Linear Mixed Effects Models},
    author = {Alexandra Kuznetsova and Per B. Brockhoff and Rune H. B.
      Christensen},
    journal = {Journal of Statistical Software},
    year = {2017},
    volume = {82},
    number = {13},
    pages = {1--26},
    doi = {10.18637/jss.v082.i13},
  }--> 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) on the basis of the null model. <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ? Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist? -->
Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
